PAMELA: an annotation-based Java Modeling Framework

### 2021-02-17 2-Abstract.tex
abstract after Antidote

\begin{abstract}
This article presents PAMELA, an annotation-based Java Modeling framework. PAMELA provides a smooth integration between model and code and enables Java developers to handle software development both at conceptual level and at source-code level, without code transformation and/or generation, avoiding round-trip related issues.

>>>>

\begin{abstract}
This article presents PAMELA, an annotation-based Java modeling framework. PAMELA provides a smooth integration between model and code and enables Java developers to handle software development both at conceptual level and at source-code level, without code transformation and/or generation, avoiding round-trip-related issues.
